RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-24 manuscripts/manuscript.Rmd
corrected capitalization
s/file/document/
recorded my doubts about having aliased method names

We begin by reading in an example NeXML file provided with the package.[^2]

@@

Previously, this was possible using the `treebase` package `r citep("Boettiger Temple Lang treebase 2012")`.
for R, which relied on the NEXUS parser provided in the `ape` package.
Due to inconsistencies present in the NEXUS standard `r citep("Vos NeXML 2012")`, 
a significant number <!-- State explicitly --> of TreeBASE NEXUS
files could not be read in this way.  Using the more precisely defined
NEXML standard, every valid NeXML file on TreeBASE can now successfully
be parsed to R objects.

>>>>

<!-- I still question the wisdom of having multiple names for the same
method. At first this might seem user-friendly, but it will just be confusing
and create a document and source code maintenance nightmare. Why not just pick
read.nexml and be done with it? -->
We begin by reading in an example NeXML file provided with the package.[^2]

@@

Previously, this was possible using the `treebase` package `r citep("Boettiger Temple Lang treebase 2012")`.
for R, which relied on the NEXUS parser provided in the `ape` package.
Due to inconsistencies present in the NEXUS standard `r citep("Vos NeXML 2012")`, 
a significant number <!-- State explicitly --> of TreeBASE NEXUS
files could not be read in this way.  Using the more precisely defined
NeXML standard, every valid NeXML document on TreeBASE can now successfully
be parsed to R objects.
